\textbf{ Spectrophotometric parallaxes with \project{The Cygnet}:\\ Accurate estimates of luminosity and distance\\ for luminous red-giant stars }

### 2018-08-01 paper/sp.tex
affiliations

\title{\textbf{%
Spectrophotometric parallax:\\
Accurate estimates of luminosity and distance\\
for luminous red-giant stars
}}

\author[0000-0003-2866-9403]{David W. Hogg}
\affiliation{Center for Cosmology and Particle Physics, Department of Physics, New York University}
\affiliation{Center for Data Science, New York University}
\affiliation{Max-Planck-Institut f\"ur Astronomie}
\affiliation{Flatiron Institute}

\author[0000-0003-2895-6218]{Anna-Christina Eilers}
\affiliation{Max-Planck-Institut f\"ur Astronomie}

\author[0000-0003-4996-9069]{Hans-Walter Rix}
\affiliation{Max-Planck-Institut f\"ur Astronomie}

>>>>

\title{\textbf{%
Spectrophotometric parallaxes with \project{The Cygnet}:\\
Accurate estimates of luminosity and distance\\
for luminous red-giant stars
}}

\author[0000-0003-2866-9403]{David W. Hogg}
\affiliation{Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, New York, NY 10003, USA}
\affiliation{Center for Data Science, New York University, 60 Fifth Ave, New York, NY 10011}
\affiliation{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, 69117 Heidelberg, Germany}
\affiliation{Flatiron Institute, 162 Fifth Ave, New York, NY 10010, USA}

\author[0000-0003-2895-6218]{Anna-Christina Eilers}
\affiliation{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, 69117 Heidelberg, Germany}
\affiliation{International Max Planck Research School for Astronomy \& Cosmic Physics at the University of Heidelberg}

\author[0000-0003-4996-9069]{Hans-Walter Rix}
\affiliation{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, 69117 Heidelberg, Germany}
